Should geophysicists use the gravity disturbance or the anomaly?

### 2018-08-29 manuscript/letter.tex
include references of Vajda

We present a discussion of whether the gravity disturbance or the gravity
anomaly should be used in geophysical applications.
The concepts discussed here are well-established in the literature and
are familiar to most geodesists.
However, the debate around this theoretical issue has been
carried about from a more geodetic than a geophysical point of view
\citep{lafehr1991,chapin1996,li2001,fairhead2003,
hackney-featherstone2003,hinze2005} and maybe that is why it is
unfamiliar to most exploration geophysicists.
We will approach the topic by comparing the geophysical interpretations of the
disturbance and the anomaly.
Our reasoning suggests that the gravity disturbance is more appropriated for
geophysical purposes than the gravity anomaly.

>>>>

We present a discussion of whether the gravity disturbance or the gravity
anomaly should be used in geophysical applications.
The concepts discussed here are well-established in the literature and
are familiar to most geodesists.
However, the debate around this theoretical issue has been
carried about from a more geodetic than a geophysical point of view
\citep{lafehr1991,chapin1996,li2001,fairhead2003,
hackney-featherstone2003,hinze2005, vajda-etal2006, vajda-etal2007, 
vajda-etal2008} and maybe that is why it is
unfamiliar to most exploration geophysicists.
We will approach the topic by comparing the geophysical interpretations of the
disturbance and the anomaly.
Our reasoning suggests that the gravity disturbance is more appropriated for
geophysical purposes than the gravity anomaly.
